---
title: "01 Data Inspection"
format: html
execute:
  echo: true
  warning: false
  message: false
---

# Purpose

This notebook performs an initial inspection of the raw Bahrami2020 four-arm restless bandit dataset.

# Dataset

- Dataset: Bahrami2020 Four-Arm Restless Bandit
- Source: OSF (https://osf.io/f3t2a/)
- File: `data/raw/DataAllSubjectsRewards.csv`

# Setup

```{r}

library(here)

source(here("R", "preprocessing.R"))
```

# Load Dataset

```{r}
raw_data <- load_raw_data()
```

# Dataset Overview

## Dimensions

```{r}
get_dimensions(raw_data)
```

## Structure

```{r}
get_structure(raw_data)
```

## Variable Names

```{r}
get_variable_names(raw_data)
```

## First Observations

```{r}
get_head(raw_data)
```

## Last Observations

```{r}
get_tail(raw_data)
```

# Variable Summary

```{r}
get_summary(raw_data)
```

# Missing Data

## Missing Values by Variable

```{r}
missing_by_variable(raw_data)
```

## Total Missing Values

```{r}
total_missing(raw_data)
```

# Participants

## Number of Participants

```{r}
participant_count(raw_data)
```

## Trials per Participant

```{r}
participant_trial_summary(raw_data)
```

# Variables

## Variable Types

```{r}
variable_types(raw_data)
```

## Unique Values

```{r}
unique_value_counts(raw_data)
```

## Payoff Groups

```{r}
payoff_groups(raw_data)
```

## Choice Values

```{r}
choice_values(raw_data)
```

# Descriptive Statistics

```{r}
behavioural_summary(raw_data)
```

# Data Integrity

## Duplicate Rows

```{r}
duplicate_rows(raw_data)
```

## Missing Participant IDs

```{r}
missing_participant_ids(raw_data)
```

## Participant Trial Distribution

```{r}
participant_trial_distribution(raw_data)
```

## Reward Range

```{r}
reward_range(raw_data)
```

## Reaction Time Range

```{r}
reaction_time_range(raw_data)
```

# Inspection Summary

```{r}
inspection_summary(raw_data)
```

# Computational Environment

```{r}
sessionInfo()
```