---
title: "Exploratory Analysis"
format: html
execute:
  echo: true
  warning: false
  message: false
---

# Purpose

This notebook performs descriptive exploratory analysis of the Bahrami2020 four-arm restless bandit dataset. The objective is to characterize behavioural patterns, evaluate the hierarchical structure of the data, assess data quality, examine variables relevant to the planned mixed-effects models, and determine readiness for statistical modelling. No confirmatory statistical inference is conducted.

# Dataset

- Dataset: Bahrami2020 Four-Arm Restless Bandit
- Source: OSF (https://osf.io/f3t2a/)

# Setup

```{r}
library(here)

source(here("R", "preprocessing.R"))
source(here("R", "visualization.R"))
```

# Load Processed Dataset

```{r}
raw_data <- load_raw_data()

nonresponse_trial_summary(raw_data)

processed_data <- preprocess_data(raw_data)

save_processed_data(processed_data)

processed_data <- load_processed_data()
```

# Dataset Verification

## Verification Summary

```{r}
verify_dataset(processed_data)
```

# Participant Characteristics

## Number of Participants

```{r}
participant_count(processed_data)
```

## Trials per Participant

```{r}
participant_trial_summary(processed_data)
```

## Participant Trial Distribution

```{r}
participant_trial_distribution(processed_data)
```

## Participant Summary

```{r}
participant_summary(processed_data)
```

## Payoff Group Summary

```{r}
payoff_group_summary(processed_data)
```

## Payoff Group Distribution

```{r}
plot_payoff_groups(processed_data)
```

## Trial Count Distribution

```{r}
plot_trial_counts(processed_data)
```

# Behavioural Variables

## Overall Behavioural Summary

```{r}
behavioural_summary(processed_data)
```

## Reward Summary

```{r}
variable_summary(processed_data, reward)
```

## Reaction Time Summary

```{r}
variable_summary(processed_data, rt)
```

## Reward Distribution

```{r}
plot_reward_distribution(processed_data)
```

## Reaction Time Distribution

```{r}
plot_rt_distribution(processed_data)
```

## Choice Distribution

```{r}
plot_choice_distribution(processed_data)
```

## Reward Boxplot

```{r}
plot_reward_boxplot(processed_data)
```

## Reaction Time Boxplot

```{r}
plot_rt_boxplot(processed_data)
```

# Learning Behaviour

## Reward Learning Curve

```{r}
plot_reward_learning_curve(processed_data)
```

## Reaction Time Learning Curve

```{r}
plot_rt_learning_curve(processed_data)
```

## Reward Learning by Payoff Group

```{r}
plot_reward_by_payoff_group(processed_data)
```

# Individual Learning Trajectories

## Reward Trajectories

```{r}
plot_individual_reward_trajectories(processed_data)
```

## Reaction Time Trajectories

```{r}
plot_individual_rt_trajectories(processed_data)
```

# Between-Participant Variability

## Mean Reward Distribution

```{r}
plot_participant_mean_reward(processed_data)
```

## Mean Reaction Time Distribution

```{r}
plot_participant_mean_rt(processed_data)
```

# Relationships Among Variables

## Reward Across Trials

```{r}
plot_reward_vs_trial(processed_data)
```

## Reaction Time Across Trials

```{r}
plot_rt_vs_trial(processed_data)
```

## Reward versus Reaction Time

```{r}
plot_reward_vs_rt(processed_data)
```

## Correlation Matrix

```{r}
plot_correlation_matrix(
        processed_data,
        variables = c(
                "reward",
                "rt",
                "trial"
        )
)
```

# Missing Data

## Missing Values by Variable

```{r}
missing_by_variable(processed_data)
```

## Missing Values by Variable (%)

```{r}
missing_by_variable_percent(processed_data)
```

## Missing Values by Participant

```{r}
missing_by_participant(processed_data)
```

## Missing Data Visualisation

```{r}
plot_missing_values(processed_data)
```

# Outlier Assessment

## Reaction Time Outliers

```{r}
reaction_time_outliers(processed_data)
```

## Reward Outliers

```{r}
reward_outliers(processed_data)
```

## Reaction Time Outlier Visualisation

```{r}
plot_rt_outliers(processed_data)
```

# Correlation Matrix

## Continuous Variables

```{r}
continuous_correlations(processed_data)
```

# Model Readiness

```{r}
model_readiness(processed_data)
```

# Computational Environment

```{r}
sessionInfo()
```