---
title: "Modeling"
format: html
execute:
  echo: true
  warning: false
  message: false
---

# Setup

```{r}
library(tidyverse)
library(lme4)
library(lmerTest)
library(broom.mixed)
library(performance)
library(DHARMa)

source("../R/preprocessing.R")
source("../R/models.R")
source("../R/visualization.R")

processed_data <- readr::read_csv(
        "../data/processed/processed_data.csv"
)
```

# Primary Outcome: Optimal Choice

## Model Fitting

```{r}
optimal_null <-
        fit_optimal_choice_null(
                processed_data
        )

optimal_fixed <-
        fit_optimal_choice_fixed(
                processed_data
        )

optimal_random_slope <-
        fit_optimal_choice_random_slope(
                processed_data
        )

optimal_interaction <-
        fit_optimal_choice_interaction(
                processed_data
        )
```

## Model Validation

```{r}
model_summary(optimal_null)

model_summary(optimal_fixed)

model_summary(optimal_random_slope)

model_summary(optimal_interaction)


check_convergence(
        optimal_interaction
)

check_singularity(
        optimal_interaction
)
```

## Model Comparison

```{r}
optimal_comparison <-
        compare_models(
                null = optimal_null,
                fixed = optimal_fixed,
                random_slope = optimal_random_slope,
                interaction = optimal_interaction
        )

optimal_comparison
```

```{r}
compare_nested_models(
        optimal_null,
        optimal_fixed,
        test = "Chisq"
)

compare_nested_models(
        optimal_fixed,
        optimal_random_slope,
        test = "Chisq"
)

compare_nested_models(
        optimal_random_slope,
        optimal_interaction,
        test = "Chisq"
)
```

## Diagnostic Evaluation

```{r}
optimal_dharma <-
        DHARMa::simulateResiduals(
                fittedModel = optimal_interaction
        )

plot(optimal_dharma)

DHARMa::testDispersion(
        optimal_dharma
)
```

## Visualization

```{r}
plot_predictions_by_group(
        optimal_interaction,
        terms = c("trial_c", "payoff_group"),
        y_label = "Predicted probability of optimal choice"
)


plot_random_intercepts(
        optimal_interaction
)


plot_random_slopes(
        optimal_interaction
)
```

# Secondary Outcome: Reward

## Model Fitting

```{r}
reward_null <-
        fit_reward_null(
                processed_data
        )

reward_fixed <-
        fit_reward_fixed(
                processed_data
        )

reward_random_slope <-
        fit_reward_random_slope(
                processed_data
        )

reward_interaction <-
        fit_reward_interaction(
                processed_data
        )
```

## Model Validation

```{r}
model_summary(reward_null)

model_summary(reward_fixed)

model_summary(reward_random_slope)

model_summary(reward_interaction)


check_convergence(
        reward_interaction
)

check_singularity(
        reward_interaction
)
```

## Model Comparison

```{r}
reward_comparison <-
        compare_models(
                null = reward_null,
                fixed = reward_fixed,
                random_slope = reward_random_slope,
                interaction = reward_interaction
        )

reward_comparison
```

```{r}
compare_nested_models(
        reward_null,
        reward_fixed
)

compare_nested_models(
        reward_fixed,
        reward_random_slope
)

compare_nested_models(
        reward_random_slope,
        reward_interaction
)
```

## Diagnostics

```{r}
plot_lmm_residuals(
        reward_interaction
)


plot_lmm_qq(
        reward_interaction
)
```

## Visualization

```{r}
plot_predictions_by_group(
        reward_interaction,
        terms = c("trial_c", "payoff_group"),
        y_label = "Predicted reward"
)
```

# Secondary Outcome: Reaction Time

## Model Fitting

```{r}
log_rt_null <-
        fit_log_rt_null(
                processed_data
        )

log_rt_fixed <-
        fit_log_rt_fixed(
                processed_data
        )

log_rt_random_slope <-
        fit_log_rt_random_slope(
                processed_data
        )

log_rt_interaction <-
        fit_log_rt_interaction(
                processed_data
        )
```

## Model Validation

```{r}
model_summary(log_rt_null)

model_summary(log_rt_fixed)

model_summary(log_rt_random_slope)

model_summary(log_rt_interaction)


check_convergence(
        log_rt_interaction
)

check_singularity(
        log_rt_interaction
)
```

## Model Comparison

```{r}
log_rt_comparison <-
        compare_models(
                null = log_rt_null,
                fixed = log_rt_fixed,
                random_slope = log_rt_random_slope,
                interaction = log_rt_interaction
        )

log_rt_comparison
```

```{r}
compare_nested_models(
        log_rt_null,
        log_rt_fixed
)

compare_nested_models(
        log_rt_fixed,
        log_rt_random_slope
)

compare_nested_models(
        log_rt_random_slope,
        log_rt_interaction
)
```

## Diagnostics

```{r}
plot_lmm_residuals(
        log_rt_interaction
)


plot_lmm_qq(
        log_rt_interaction
)
```

## Visualization

```{r}
plot_predictions_by_group(
        log_rt_interaction,
        terms = c("trial_c", "payoff_group"),
        y_label = "Predicted log reaction time"
)
```

# Secondary Outcome: Choice Switching

## Model Fitting

```{r}
switch_null <-
        fit_choice_switch_null(
                processed_data
        )

switch_fixed <-
        fit_choice_switch_fixed(
                processed_data
        )

switch_random_slope <-
        fit_choice_switch_random_slope(
                processed_data
        )

switch_interaction <-
        fit_choice_switch_interaction(
                processed_data
        )
```

## Model Validation

```{r}
model_summary(switch_null)

model_summary(switch_fixed)

model_summary(switch_random_slope)

model_summary(switch_interaction)


check_convergence(
        switch_interaction
)

check_singularity(
        switch_interaction
)
```

## Model Comparison

```{r}
switch_comparison <-
        compare_models(
                null = switch_null,
                fixed = switch_fixed,
                random_slope = switch_random_slope,
                interaction = switch_interaction
        )

switch_comparison
```

```{r}
compare_nested_models(
        switch_null,
        switch_fixed,
        test = "Chisq"
)

compare_nested_models(
        switch_fixed,
        switch_random_slope,
        test = "Chisq"
)

compare_nested_models(
        switch_random_slope,
        switch_interaction,
        test = "Chisq"
)
```

## Diagnostics

```{r}
switch_dharma <-
        DHARMa::simulateResiduals(
                fittedModel = switch_interaction
        )

plot(switch_dharma)

DHARMa::testDispersion(
        switch_dharma
)
```

## Visualization

```{r}
plot_predictions_by_group(
        switch_interaction,
        terms = c("trial_c", "payoff_group"),
        y_label = "Predicted probability of switching"
)
```

# Robustness Analyses

## Quadratic Learning Model

```{r}
optimal_quadratic <-
        fit_optimal_choice_quadratic(
                processed_data
        )


quadratic_comparison <-
        compare_models(
                linear = optimal_interaction,
                quadratic = optimal_quadratic
        )

quadratic_comparison
```

## Random-Effects Sensitivity

```{r}
optimal_correlated_slope <-
        fit_optimal_choice_random_slope(
                processed_data
        )


random_effect_comparison <-
        compare_models(
                uncorrelated = optimal_random_slope,
                correlated = optimal_correlated_slope
        )

random_effect_comparison
```

# Fixed Effects Reporting

```{r}
optimal_effects <-
        broom.mixed::tidy(
                optimal_interaction,
                effects = "fixed",
                conf.int = TRUE
        )


reward_effects <-
        broom.mixed::tidy(
                reward_interaction,
                effects = "fixed",
                conf.int = TRUE
        )


log_rt_effects <-
        broom.mixed::tidy(
                log_rt_interaction,
                effects = "fixed",
                conf.int = TRUE
        )


switch_effects <-
        broom.mixed::tidy(
                switch_interaction,
                effects = "fixed",
                conf.int = TRUE
        )


optimal_effects
reward_effects
log_rt_effects
switch_effects
```
# Computational Environment

```{r}
sessionInfo()
```
