---
title: "Modeling"
format: html
execute:
  echo: true
  warning: false
  message: false
---

# Purpose

This notebook performs the prespecified mixed-effects modeling analyses of the processed Bahrami2020 four-arm bandit task dataset. It evaluates trial-wise performance trajectories, individual differences, model fit, and robustness across alternative model specifications.

# Dataset

- Dataset: 4 Arm Bandit Task Dataset
- Source: OSF (https://osf.io/f3t2a/)

# Setup

```{r}
library(tidyverse)
library(lme4)
library(lmerTest)
library(broom.mixed)
library(performance)
library(DHARMa)

source("../R/preprocessing.R")
source("../R/models.R")
source("../R/visualization.R")

raw_data <- load_raw_data()

processed_data <- load_processed_data()
```

# Create Results Directory

```{r}

dir.create(
        here::here(
                "results",
                "tables"
        ),
        recursive = TRUE,
        showWarnings = FALSE
)

dir.create(
        here::here(
                "results",
                "figures"
        ),
        recursive = TRUE,
        showWarnings = FALSE
)

dir.create(
        here::here(
                "results",
                "models"
        ),
        recursive = TRUE,
        showWarnings = FALSE
)

dir.create(
        here::here(
                "results",
                "figures",
                "diagnostics"
        ),
        recursive = TRUE,
        showWarnings = FALSE
)

```

# Participant Retention Audit

```{r}
participant_retention <-
        participant_retention_summary(
                raw_data = raw_data,
                processed_data = processed_data
        )

participant_retention

readr::write_csv(
        participant_retention,
        here::here(
                "results",
                "tables",
                "participant-retention-summary.csv"
        )
)

participant_retention_details <-
        participant_retention_details(
                raw_data = raw_data,
                processed_data = processed_data
        )

participant_retention_details

readr::write_csv(
        participant_retention_details,
        here::here(
                "results",
                "tables",
                "participant-retention-details.csv"
        )
)
```

# Primary Outcome: Payoff Maximizing Choice

## Ensure Appropriate Factor Coding

```{r}
processed_data <- processed_data |>
        convert_payoff_group()
```

## Model Fitting

```{r}
payoff_maximizing_null <-
        fit_payoff_maximizing_choice_null(
                processed_data
        )

payoff_maximizing_fixed <-
        fit_payoff_maximizing_choice_fixed(
                processed_data
        )

payoff_maximizing_random_slope_uncorrelated <-
        fit_payoff_maximizing_choice_random_slope_uncorrelated(
                processed_data
        )

payoff_maximizing_random_slope_correlated <-
        fit_payoff_maximizing_choice_random_slope_correlated(
                processed_data
        )

payoff_maximizing_interaction <-
        fit_payoff_maximizing_choice_interaction(
                processed_data
        )
```

## Model Validation

```{r}
model_summary(payoff_maximizing_null)

model_summary(payoff_maximizing_fixed)

model_summary(payoff_maximizing_random_slope_uncorrelated)

model_summary(payoff_maximizing_random_slope_correlated)

model_summary(payoff_maximizing_interaction)


model_convergence(payoff_maximizing_interaction)

model_singularity(payoff_maximizing_interaction)


payoff_maximizing_export <-
        export_model_summary(payoff_maximizing_interaction)
```

## Model Comparison

```{r}
payoff_maximizing_comparison <-
        compare_models(
                null = payoff_maximizing_null,
                fixed = payoff_maximizing_fixed,
                random_slope = payoff_maximizing_random_slope_uncorrelated,
                random_slope_correlated = payoff_maximizing_random_slope_correlated,
                interaction = payoff_maximizing_interaction
        )

payoff_maximizing_comparison
```

```{r}
compare_nested_models(
        payoff_maximizing_null,
        payoff_maximizing_fixed,
)

compare_nested_models(
        payoff_maximizing_fixed,
        payoff_maximizing_random_slope_uncorrelated,
)

compare_nested_models(
        payoff_maximizing_random_slope_uncorrelated,
        payoff_maximizing_interaction,
)
```

## Visualization

```{r}
plot_predictions_by_group(
        payoff_maximizing_interaction,
        y_label = "Predicted probability of payoff-maximizing choice"
)


plot_random_intercepts(
        payoff_maximizing_interaction
)


plot_random_slopes(
        payoff_maximizing_interaction
)
```

# Secondary Outcome: Reward

## Model Fitting

```{r}
reward_null <-
        fit_reward_null(
                processed_data
        )

reward_fixed <-
        fit_reward_fixed(
                processed_data
        )

reward_random_slope <-
        fit_reward_random_slope(
                processed_data
        )

reward_interaction <-
        fit_reward_interaction(
                processed_data
        )
```

## Model Validation

```{r}
model_summary(reward_null)

model_summary(reward_fixed)

model_summary(reward_random_slope)

model_summary(reward_interaction)


model_convergence(reward_interaction)

model_singularity(reward_interaction)


reward_export <-
        export_model_summary(reward_interaction)
```

## Model Comparison

```{r}
reward_comparison <-
        compare_models(
                null = reward_null,
                fixed = reward_fixed,
                random_slope = reward_random_slope,
                interaction = reward_interaction
        )

reward_comparison
```

```{r}
compare_nested_models(
        reward_null,
        reward_fixed
)

compare_nested_models(
        reward_fixed,
        reward_random_slope
)

compare_nested_models(
        reward_random_slope,
        reward_interaction
)
```

## Diagnostics

```{r}
plot_lmm_residuals(
        reward_interaction
)


plot_lmm_qq(
        reward_interaction
)
```

## Visualization

```{r}
plot_predictions_by_group(
        reward_interaction,
        y_label = "Predicted reward"
)
```

# Secondary Outcome: Reaction Time

## Model Fitting

```{r}
log_rt_null <-
        fit_log_rt_null(
                processed_data
        )

log_rt_fixed <-
        fit_log_rt_fixed(
                processed_data
        )

log_rt_random_slope <-
        fit_log_rt_random_slope(
                processed_data
        )

log_rt_interaction <-
        fit_log_rt_interaction(
                processed_data
        )
```

## Model Validation

```{r}
model_summary(log_rt_null)

model_summary(log_rt_fixed)

model_summary(log_rt_random_slope)

model_summary(log_rt_interaction)


model_convergence(log_rt_random_slope)

model_singularity(log_rt_random_slope)


log_rt_export <-
        export_model_summary(log_rt_random_slope)
```

## Model Comparison

```{r}
log_rt_comparison <-
        compare_models(
                null = log_rt_null,
                fixed = log_rt_fixed,
                random_slope = log_rt_random_slope,
                interaction = log_rt_interaction
        )

log_rt_comparison
```

```{r}
compare_nested_models(
        log_rt_null,
        log_rt_fixed
)

compare_nested_models(
        log_rt_fixed,
        log_rt_random_slope
)

compare_nested_models(
        log_rt_random_slope,
        log_rt_interaction
)
```

## Diagnostics

```{r}
plot_lmm_residuals(log_rt_random_slope)


plot_lmm_qq(log_rt_random_slope)
```

## Visualization

```{r}
plot_predictions_by_group(
        log_rt_random_slope,
        y_label = "Predicted log reaction time"
)
```

# Secondary Outcome: Choice Switching

## Model Fitting

```{r}
switch_null <-
        fit_choice_switch_null(
                processed_data
        )

switch_fixed <-
        fit_choice_switch_fixed(
                processed_data
        )

switch_random_slope <-
        fit_choice_switch_random_slope(
                processed_data
        )

switch_interaction <-
        fit_choice_switch_interaction(
                processed_data
        )
```

## Model Validation

```{r}
model_summary(switch_null)

model_summary(switch_fixed)

model_summary(switch_random_slope)

model_summary(switch_interaction)


model_convergence(switch_interaction)

model_singularity(switch_interaction)


choice_switch_export <-
        export_model_summary(switch_interaction)
```

## Model Comparison

```{r}
switch_comparison <-
        compare_models(
                null = switch_null,
                fixed = switch_fixed,
                random_slope = switch_random_slope,
                interaction = switch_interaction
        )

switch_comparison
```

```{r}
compare_nested_models(
        switch_null,
        switch_fixed,
)

compare_nested_models(
        switch_fixed,
        switch_random_slope,
)

compare_nested_models(
        switch_random_slope,
        switch_interaction,
)
```

## Diagnostics

```{r}
switch_dharma <-
        DHARMa::simulateResiduals(
                fittedModel = switch_interaction
        )

plot(switch_dharma)

DHARMa::testDispersion(
        switch_dharma
)
```

## Visualization

```{r}
plot_predictions_by_group(
        switch_interaction,
        y_label = "Predicted probability of switching"
)
```

# Primary Model Selection

## Linear vs Quadratic Trial Trajectory

```{r}
payoff_maximizing_quadratic_uncorrelated <-
        fit_payoff_maximizing_choice_quadratic_uncorrelated(
                processed_data
        )

payoff_maximizing_quadratic_correlated <-
        fit_payoff_maximizing_choice_quadratic_correlated(
                processed_data
        )


quadratic_comparison <-
        compare_models(
                linear_interaction = payoff_maximizing_interaction,
                quadratic_uncorrelated = payoff_maximizing_quadratic_uncorrelated,
                quadratic_correlated = payoff_maximizing_quadratic_correlated
        ) |>
        dplyr::mutate(
                delta_AIC = AIC - min(AIC)
        )

quadratic_comparison
```

```{r}
payoff_maximizing_linear_interaction_robustness <-
        fit_payoff_maximizing_interaction_quadratic_data(
                processed_data
        )

payoff_maximizing_linear_vs_quadratic <-
        compare_models(
                linear = payoff_maximizing_linear_interaction_robustness,
                quadratic = payoff_maximizing_quadratic_uncorrelated
        ) |>
        dplyr::mutate(
                delta_AIC = AIC - min(AIC)
        )

payoff_maximizing_linear_vs_quadratic

payoff_maximizing_quadratic_likelihood_ratio <-
        compare_nested_models(
                payoff_maximizing_linear_interaction_robustness,
                payoff_maximizing_quadratic_uncorrelated
        )

payoff_maximizing_quadratic_likelihood_ratio
```

## Random-Effects Sensitivity

```{r}
quadratic_random_effect_comparison <-
        compare_models(
                uncorrelated = payoff_maximizing_quadratic_uncorrelated,
                correlated = payoff_maximizing_quadratic_correlated
        ) |>
        dplyr::mutate(
                delta_AIC = AIC - min(AIC)
        )

quadratic_random_effect_comparison

quadratic_random_effect_likelihood_ratio <-
    compare_nested_models(
        payoff_maximizing_quadratic_uncorrelated,
        payoff_maximizing_quadratic_correlated
    )

quadratic_random_effect_likelihood_ratio
```

# Final Model Validation

```{r}
model_convergence(payoff_maximizing_quadratic_uncorrelated)
model_singularity(payoff_maximizing_quadratic_uncorrelated)
model_summary(payoff_maximizing_quadratic_uncorrelated)

model_convergence(payoff_maximizing_quadratic_correlated)
model_singularity(payoff_maximizing_quadratic_correlated)
model_summary(payoff_maximizing_quadratic_correlated)

model_convergence(reward_interaction)
model_singularity(reward_interaction)
model_summary(reward_interaction)

model_convergence(log_rt_random_slope)
model_singularity(log_rt_random_slope)
model_summary(log_rt_random_slope)

model_convergence(switch_interaction)
model_singularity(switch_interaction)
model_summary(switch_interaction)
```

## Model Selection Criteria

The final model specification was selected based on:

- model convergence,
- absence of singular random-effects structure,
- improved model fit based on AIC, BIC, and log-likelihood,
- likelihood-ratio tests for nested model comparisons.

The quadratic specification was preferred to the linear interaction specification based on the prespecified model-comparison criteria, including AIC, BIC, and the likelihood-ratio test. Among the quadratic specifications, the correlated random-effects model was retained based on comparative model fit (AIC, BIC, and log-likelihood), provided that it showed no convergence failure or singularity. The final model therefore included a quadratic trial trajectory, its interaction with payoff group, and correlated participant-specific random intercepts, linear trial slopes, and quadratic trial slopes.

```{r}
payoff_maximizing_selection <-
        tibble::tibble(

                model = c(
                        "null",
                        "fixed",
                        "random_slope",
                        "linear_interaction",
                        "quadratic_uncorrelated",
                        "quadratic_correlated"
                ),

                AIC = c(
                        AIC(payoff_maximizing_null),
                        AIC(payoff_maximizing_fixed),
                        AIC(payoff_maximizing_random_slope_uncorrelated),
                        AIC(payoff_maximizing_interaction),
                        AIC(payoff_maximizing_quadratic_uncorrelated),
                        AIC(payoff_maximizing_quadratic_correlated)
                ),

                BIC = c(
                        BIC(payoff_maximizing_null),
                        BIC(payoff_maximizing_fixed),
                        BIC(payoff_maximizing_random_slope_uncorrelated),
                        BIC(payoff_maximizing_interaction),
                        BIC(payoff_maximizing_quadratic_uncorrelated),
                        BIC(payoff_maximizing_quadratic_correlated)
                ),

                logLik = c(
                        as.numeric(
                                logLik(payoff_maximizing_null)
                        ),
                        as.numeric(
                                logLik(payoff_maximizing_fixed)
                        ),
                        as.numeric(
                                logLik(payoff_maximizing_random_slope_uncorrelated)
                        ),
                        as.numeric(
                                logLik(payoff_maximizing_interaction)
                        ),
                        as.numeric(
                                logLik(payoff_maximizing_quadratic_uncorrelated)
                        ),
                        as.numeric(
                                logLik(payoff_maximizing_quadratic_correlated)
                        )
                ),

                parameters = c(
                        attr(
                                logLik(payoff_maximizing_null),
                                "df"
                        ),
                        attr(
                                logLik(payoff_maximizing_fixed),
                                "df"
                        ),
                        attr(
                                logLik(payoff_maximizing_random_slope_uncorrelated),
                                "df"
                        ),
                        attr(
                                logLik(payoff_maximizing_interaction),
                                "df"
                        ),
                        attr(
                                logLik(payoff_maximizing_quadratic_uncorrelated),
                                "df"
                        ),
                        attr(
                                logLik(payoff_maximizing_quadratic_correlated),
                                "df"
                        )
                ),

                delta_AIC = AIC - min(AIC),

                singular = c(
                        model_singularity(
                                payoff_maximizing_null
                        ),
                        model_singularity(
                                payoff_maximizing_fixed
                        ),
                        model_singularity(
                                payoff_maximizing_random_slope_uncorrelated
                        ),
                        model_singularity(
                                payoff_maximizing_interaction
                        ),
                        model_singularity(
                                payoff_maximizing_quadratic_uncorrelated
                        ),
                        model_singularity(
                                payoff_maximizing_quadratic_correlated
                        )
                ),

                convergence = c(
                        model_convergence(
                                payoff_maximizing_null
                        ),
                        model_convergence(
                                payoff_maximizing_fixed
                        ),
                        model_convergence(
                                payoff_maximizing_random_slope_uncorrelated
                        ),
                        model_convergence(
                                payoff_maximizing_interaction
                        ),
                        model_convergence(
                                payoff_maximizing_quadratic_uncorrelated
                        ),
                        model_convergence(
                                payoff_maximizing_quadratic_correlated
                        )
                )
        )

payoff_maximizing_selection
```

# Final Model Selection

```{r}

final_payoff_maximizing_choice_model <- payoff_maximizing_quadratic_correlated

final_reward_model <- reward_interaction

final_log_rt_model <- log_rt_random_slope

final_choice_switch_model <- switch_interaction

final_model_specifications <-
        tibble::tibble(
                outcome = c(
                        "payoff_maximizing_choice",
                        "reward",
                        "log_rt",
                        "choice_switch"
                ),
                formula = c(
                        paste(
                                deparse(
                                        formula(
                                                final_payoff_maximizing_choice_model
                                        )
                                ),
                                collapse = " "
                        ),
                        paste(
                                deparse(
                                        formula(final_reward_model)
                                ),
                                collapse = " "
                        ),
                        paste(
                                deparse(
                                        formula(final_log_rt_model)
                                ),
                                collapse = " "
                        ),
                        paste(
                                deparse(
                                        formula(final_choice_switch_model)
                                ),
                                collapse = " "
                        )
                )
        )

readr::write_csv(
        final_model_specifications,
        here::here(
                "results",
                "tables",
                "final-model-specifications.csv"
        )
)

```

# Save Final Models

```{r}
saveRDS(
        final_payoff_maximizing_choice_model,
        here::here(
                "results",
                "models",
                "final-payoff-maximizing-choice-model.rds"
        )
)

saveRDS(
        final_reward_model,
        here::here(
                "results",
                "models",
                "final-reward-model.rds"
        )
)

saveRDS(
        final_log_rt_model,
        here::here(
                "results",
                "models",
                "final-log-rt-model.rds"
        )
)

saveRDS(
        final_choice_switch_model,
        here::here(
                "results",
                "models",
                "final-choice-switch-model.rds"
        )
)
```

# Save Models Summary

```{r}
saveRDS(
        export_model_summary(
                payoff_maximizing_quadratic_uncorrelated
        ),
        here::here(
                "results",
                "models",
                "payoff-maximizing-quadratic-uncorrelated-model-summary.rds"
        )
)

saveRDS(
        export_model_summary(
                payoff_maximizing_quadratic_correlated
        ),
        here::here(
                "results",
                "models",
                "payoff-maximizing-quadratic-correlated-model-summary.rds"
        )
)

saveRDS(
    export_model_summary(final_reward_model),
    here::here(
        "results",
        "models",
        "reward-model-summary.rds"
    )
)

saveRDS(
    export_model_summary(final_log_rt_model),
    here::here(
        "results",
        "models",
        "log-rt-model-summary.rds"
    )
)

saveRDS(
    export_model_summary(final_choice_switch_model),
    here::here(
        "results",
        "models",
        "choice-switch-model-summary.rds"
    )
)
```

# Descriptive Statistics

```{r}
descriptive_statistics <-
        descriptive_statistics_table(
                processed_data
        )

payoff_group_statistics <-
        payoff_group_summary(
                processed_data
        )

descriptive_statistics

payoff_group_statistics
```

```{r}
choice_switch_missingness <-
    choice_switch_missingness_summary(
        processed_data
    )

choice_switch_missingness_summary_table <-
    audit_choice_switch_missingness(
        processed_data
    )

choice_switch_missingness_summary_table

readr::write_csv(
    choice_switch_missingness_summary_table,
    here::here(
        "results",
        "tables",
        "choice-switch-missingness-summary.csv"
    )
)
```

```{r}
readr::write_csv(
        descriptive_statistics,
        here::here(
                "results",
                "tables",
                "descriptive-statistics.csv"
        )
)

readr::write_csv(
        payoff_group_statistics,
        here::here(
                "results",
                "tables",
                "payoff-group-statistics.csv"
        )
)
```

# Reward Distribution

```{r}
reward_distribution <-
        plot_reward_distribution(
                processed_data
        )

reward_distribution
```

# Log Reaction Time Distribution

```{r}
log_rt_distribution <-
        plot_log_rt_distribution(
                processed_data
        )

log_rt_distribution
```

# Choice Distribution

```{r}
choice_distribution <-
        plot_choice_distribution(
                processed_data
        )

choice_distribution
```

# Choice Switching Distribution

```{r}
switch_distribution <-
        plot_switch_distribution(
                processed_data
        )

switch_distribution
```

# Export Descriptive Figures

```{r}
ggplot2::ggsave(
        filename = here::here(
                "results",
                "figures",
                "reward-distribution.pdf"
        ),
        plot = reward_distribution,
        width = 6,
        height = 4
)

ggplot2::ggsave(
        filename = here::here(
                "results",
                "figures",
                "reward-distribution.png"
        ),
        plot = reward_distribution,
        width = 6,
        height = 4,
        dpi = 300
)

ggplot2::ggsave(
        filename = here::here(
                "results",
                "figures",
                "rt-distribution.pdf"
        ),
        plot = log_rt_distribution,
        width = 6,
        height = 4
)

ggplot2::ggsave(
        filename = here::here(
                "results",
                "figures",
                "rt-distribution.png"
        ),
        plot = log_rt_distribution,
        width = 6,
        height = 4,
        dpi = 300
)

ggplot2::ggsave(
        filename = here::here(
                "results",
                "figures",
                "choice-distribution.pdf"
        ),
        plot = choice_distribution,
        width = 6,
        height = 4
)

ggplot2::ggsave(
        filename = here::here(
                "results",
                "figures",
                "choice-distribution.png"
        ),
        plot = choice_distribution,
        width = 6,
        height = 4,
        dpi = 300
)

ggplot2::ggsave(
        filename = here::here(
                "results",
                "figures",
                "switch-distribution.pdf"
        ),
        plot = switch_distribution,
        width = 6,
        height = 4
)

ggplot2::ggsave(
        filename = here::here(
                "results",
                "figures",
                "switch-distribution.png"
        ),
        plot = switch_distribution,
        width = 6,
        height = 4,
        dpi = 300
)
```

# Extract Fixed Effects

```{r}
payoff_maximizing_choice_fixed_effects <-
        model_fixed_effects(
                final_payoff_maximizing_choice_model
        )

reward_fixed_effects <-
        model_fixed_effects(
                final_reward_model
        )

log_rt_fixed_effects <-
        model_fixed_effects(
                final_log_rt_model
        )

choice_switch_fixed_effects <-
        model_fixed_effects(
                final_choice_switch_model
        )

payoff_maximizing_choice_confidence_intervals <-
        model_confidence_intervals(
                final_payoff_maximizing_choice_model
        )

reward_confidence_intervals <-
        model_confidence_intervals(
                final_reward_model
        )

log_rt_confidence_intervals <-
        model_confidence_intervals(
                final_log_rt_model
        )

choice_switch_confidence_intervals <-
        model_confidence_intervals(
                final_choice_switch_model
        )

payoff_maximizing_choice_fixed_effects

reward_fixed_effects

log_rt_fixed_effects

choice_switch_fixed_effects


levels(processed_data$payoff_group)

formula(final_payoff_maximizing_choice_model)

lme4::fixef(final_payoff_maximizing_choice_model)
```

# Logistic Model Odds Ratios

```{r}
payoff_maximizing_choice_odds_ratios <-
        model_odds_ratios(
                final_payoff_maximizing_choice_model
        )

choice_switch_odds_ratios <-
        model_odds_ratios(
                final_choice_switch_model
        )


payoff_maximizing_choice_odds_ratios

choice_switch_odds_ratios
```

# Export Fixed Effects Tables

```{r}
readr::write_csv(
        payoff_maximizing_choice_fixed_effects,
        here::here(
                "results",
                "tables",
                "payoff-maximizing-choice-fixed-effects.csv"
        )
)

readr::write_csv(
        reward_fixed_effects,
        here::here(
                "results",
                "tables",
                "reward-fixed-effects.csv"
        )
)

readr::write_csv(
        log_rt_fixed_effects,
        here::here(
                "results",
                "tables",
                "log-rt-fixed-effects.csv"
        )
)

readr::write_csv(
        choice_switch_fixed_effects,
        here::here(
                "results",
                "tables",
                "choice-switch-fixed-effects.csv"
        )
)
```

# Export Confidence Intervals

```{r}
readr::write_csv(
        payoff_maximizing_choice_confidence_intervals,
        here::here(
                "results",
                "tables",
                "payoff-maximizing-choice-confidence-intervals.csv"
        )
)

readr::write_csv(
        reward_confidence_intervals,
        here::here(
                "results",
                "tables",
                "reward-confidence-intervals.csv"
        )
)

readr::write_csv(
        log_rt_confidence_intervals,
        here::here(
                "results",
                "tables",
                "log-rt-confidence-intervals.csv"
        )
)

readr::write_csv(
        choice_switch_confidence_intervals,
        here::here(
                "results",
                "tables",
                "choice-switch-confidence-intervals.csv"
        )
)
```

# Export Odds Ratios

```{r}
readr::write_csv(
        payoff_maximizing_choice_odds_ratios,
        here::here(
                "results",
                "tables",
                "payoff-maximizing-choice-odds-ratios.csv"
        )
)

readr::write_csv(
        choice_switch_odds_ratios,
        here::here(
                "results",
                "tables",
                "choice-switch-odds-ratios.csv"
        )
)
```

# Random-Effects Variance Summary

```{r}
payoff_maximizing_choice_random_effects <-
        extract_random_effects(
                final_payoff_maximizing_choice_model,
                "payoff_maximizing_choice"
        )


reward_random_effects <-
        extract_random_effects(
                final_reward_model,
                "reward"
        )


log_rt_random_effects <-
        extract_random_effects(
                final_log_rt_model,
                "log_rt"
        )


choice_switch_random_effects <-
        extract_random_effects(
                final_choice_switch_model,
                "choice_switch"
        )


random_effects_summary <-
        dplyr::bind_rows(
                payoff_maximizing_choice_random_effects,
                reward_random_effects,
                log_rt_random_effects,
                choice_switch_random_effects
        )


random_effects_summary
```

# Export Random-Effects Summary

```{r}
readr::write_csv(
        random_effects_summary,
        here::here(
                "results",
                "tables",
                "random-effects-summary.csv"
        )
)
```

# Primary Model Random-Effects Distributions

```{r}
payoff_maximizing_choice_random_intercepts <-
        plot_random_intercepts(
                final_payoff_maximizing_choice_model
        )


payoff_maximizing_choice_random_slopes <-
        plot_random_slopes(
                final_payoff_maximizing_choice_model
        )


payoff_maximizing_choice_random_intercepts

payoff_maximizing_choice_random_slopes
```

# Export Random-Effects Figures

```{r}
ggplot2::ggsave(
        filename = here::here(
                "results",
                "figures",
                "random-intercepts-payoff-maximizing-choice.pdf"
        ),
        plot = payoff_maximizing_choice_random_intercepts,
        width = 6,
        height = 4
)


ggplot2::ggsave(
        filename = here::here(
                "results",
                "figures",
                "random-intercepts-payoff-maximizing-choice.png"
        ),
        plot = payoff_maximizing_choice_random_intercepts,
        width = 6,
        height = 4,
        dpi = 300
)


ggplot2::ggsave(
        filename = here::here(
                "results",
                "figures",
                "random-slopes-payoff-maximizing-choice.pdf"
        ),
        plot = payoff_maximizing_choice_random_slopes,
        width = 6,
        height = 4
)


ggplot2::ggsave(
        filename = here::here(
                "results",
                "figures",
                "random-slopes-payoff-maximizing-choice.png"
        ),
        plot = payoff_maximizing_choice_random_slopes,
        width = 6,
        height = 4,
        dpi = 300
)
```

# Main Figure Export Settings

```{r}
figure_width <- 7
figure_height <- 5
figure_dpi <- 300

prediction_data <-
        processed_data |>
        center_trial()

trial_values <- seq(
        min(prediction_data$trial_c, na.rm = TRUE),
        max(prediction_data$trial_c, na.rm = TRUE),
        length.out = 100
)
```

# Figure 1: Predicted probability of payoff maximizing choice

```{r}
figure_payoff_maximizing_choice <-
        plot_predictions_by_group(
                final_payoff_maximizing_choice_model,
                trial_values = trial_values,
                y_label = "Predicted probability of payoff maximizing choice"
        )

figure_payoff_maximizing_choice
```

```{r}
ggplot2::ggsave(
        filename = here::here(
                "results",
                "figures",
                "figure-1-payoff-maximizing-choice-probability.pdf"
        ),
        plot = figure_payoff_maximizing_choice,
        width = figure_width,
        height = figure_height
)


ggplot2::ggsave(
        filename = here::here(
                "results",
                "figures",
                "figure-1-payoff-maximizing-choice-probability.png"
        ),
        plot = figure_payoff_maximizing_choice,
        width = figure_width,
        height = figure_height,
        dpi = figure_dpi
)
```

# Figure 2: Predicted reward trajectory

```{r}
figure_reward_trajectory <-
        plot_predictions_by_group(
                final_reward_model,
                trial_values = trial_values,
                y_label = "Predicted reward"
        )


figure_reward_trajectory
```

```{r}

ggplot2::ggsave(
        filename = here::here(
                "results",
                "figures",
                "figure-2-reward-trajectory.pdf"
        ),
        plot = figure_reward_trajectory,
        width = figure_width,
        height = figure_height
)


ggplot2::ggsave(
        filename = here::here(
                "results",
                "figures",
                "figure-2-reward-trajectory.png"
        ),
        plot = figure_reward_trajectory,
        width = figure_width,
        height = figure_height,
        dpi = figure_dpi
)
```

# Figure 3: Predicted log reaction time trajectory

```{r}
figure_reaction_time_trajectory <-
        plot_predictions_by_group(
                final_log_rt_model,
                trial_values = trial_values,
                y_label = "Predicted log reaction time"
        )


figure_reaction_time_trajectory
```

```{r}
ggplot2::ggsave(
        filename = here::here(
                "results",
                "figures",
                "figure-3-reaction-time-trajectory.pdf"
        ),
        plot = figure_reaction_time_trajectory,
        width = figure_width,
        height = figure_height
)


ggplot2::ggsave(
        filename = here::here(
                "results",
                "figures",
                "figure-3-reaction-time-trajectory.png"
        ),
        plot = figure_reaction_time_trajectory,
        width = figure_width,
        height = figure_height,
        dpi = figure_dpi
)
```

# Figure 4: Predicted choice-switch probability

```{r}
figure_choice_switch_probability <-
        plot_predictions_by_group(
                final_choice_switch_model,
                trial_values = trial_values,
                y_label = "Predicted probability of switching"
        )


figure_choice_switch_probability
```

```{r}
ggplot2::ggsave(
        filename = here::here(
                "results",
                "figures",
                "figure-4-choice-switch-probability.pdf"
        ),
        plot = figure_choice_switch_probability,
        width = figure_width,
        height = figure_height
)


ggplot2::ggsave(
        filename = here::here(
                "results",
                "figures",
                "figure-4-choice-switch-probability.png"
        ),
        plot = figure_choice_switch_probability,
        width = figure_width,
        height = figure_height,
        dpi = figure_dpi
)
```

# Generate Effect-Size Plots

```{r}
payoff_maximizing_odds_ratio_plot <-
        plot_odds_ratios(
                final_payoff_maximizing_choice_model
        )


reward_coefficient_plot <-
        plot_fixed_effects(
                final_reward_model
        )


log_rt_coefficient_plot <-
        plot_fixed_effects(
                final_log_rt_model
        )


switch_odds_ratio_plot <-
        plot_odds_ratios(
                final_choice_switch_model
        )


payoff_maximizing_odds_ratio_plot

reward_coefficient_plot

log_rt_coefficient_plot

switch_odds_ratio_plot
```

```{r}
effect_plots <- list(
        "payoff-maximizing-choice-odds-ratios" =
                payoff_maximizing_odds_ratio_plot,
        "reward-coefficients" =
                reward_coefficient_plot,
        "log-rt-coefficients" =
                log_rt_coefficient_plot,
        "choice-switch-odds-ratios" =
                switch_odds_ratio_plot
)


purrr::iwalk(
        effect_plots,
        function(plot_object, plot_name) {

                ggplot2::ggsave(
                        filename = here::here(
                                "results",
                                "figures",
                                paste0(
                                        plot_name,
                                        ".pdf"
                                )
                        ),
                        plot = plot_object,
                        width = figure_width,
                        height = figure_height
                )


                ggplot2::ggsave(
                        filename = here::here(
                                "results",
                                "figures",
                                paste0(
                                        plot_name,
                                        ".png"
                                )
                        ),
                        plot = plot_object,
                        width = figure_width,
                        height = figure_height,
                        dpi = figure_dpi
                )
        }
)
```

# Model Comparison Results

```{r}
payoff_maximizing_model_comparison <-
        compare_models(
                null = payoff_maximizing_null,
                fixed = payoff_maximizing_fixed,
                random_slope = payoff_maximizing_random_slope_uncorrelated,
                interaction = payoff_maximizing_interaction,
                quadratic_uncorrelated = payoff_maximizing_quadratic_uncorrelated,
                quadratic_correlated = payoff_maximizing_quadratic_correlated
        ) |>
        dplyr::mutate(
                delta_AIC = AIC - min(AIC),
                outcome = "payoff_maximizing_choice"
        )


reward_model_comparison <-
        compare_models(
                null = reward_null,
                fixed = reward_fixed,
                random_slope = reward_random_slope,
                interaction = reward_interaction
        ) |>
        dplyr::mutate(
                delta_AIC = AIC - min(AIC),
                outcome = "reward"
        )


log_rt_model_comparison <-
        compare_models(
                null = log_rt_null,
                fixed = log_rt_fixed,
                random_slope = log_rt_random_slope,
                interaction = log_rt_interaction
        ) |>
        dplyr::mutate(
                delta_AIC = AIC - min(AIC),
                outcome = "log_rt"
        )


switch_model_comparison <-
        compare_models(
                null = switch_null,
                fixed = switch_fixed,
                random_slope = switch_random_slope,
                interaction = switch_interaction
        ) |>
        dplyr::mutate(
                delta_AIC = AIC - min(AIC),
                outcome = "choice_switch"
        )
```

```{r}
readr::write_csv(
        payoff_maximizing_model_comparison,
        here::here(
                "results",
                "tables",
                "payoff-maximizing-model-comparison.csv"
        )
)


readr::write_csv(
        reward_model_comparison,
        here::here(
                "results",
                "tables",
                "reward-model-comparison.csv"
        )
)


readr::write_csv(
        log_rt_model_comparison,
        here::here(
                "results",
                "tables",
                "log-rt-model-comparison.csv"
        )
)


readr::write_csv(
        switch_model_comparison,
        here::here(
                "results",
                "tables",
                "choice-switch-model-comparison.csv"
        )
)
```

# Combined Comparison Table

```{r}
model_comparison_all_outcomes <-
        dplyr::bind_rows(
                payoff_maximizing_model_comparison,
                reward_model_comparison,
                log_rt_model_comparison,
                switch_model_comparison
        )


readr::write_csv(
        model_comparison_all_outcomes,
        here::here(
                "results",
                "tables",
                "model-comparison-all-outcomes.csv"
        )
)


model_comparison_all_outcomes
```

# Model Comparison Visualization

```{r}
payoff_maximizing_model_comparison_plot <-
        plot_model_comparison(
                payoff_maximizing_model_comparison
        )


payoff_maximizing_model_comparison_plot
```

```{r}
ggplot2::ggsave(
        filename = here::here(
                "results",
                "figures",
                "comparison-plot.pdf"
        ),
        plot = payoff_maximizing_model_comparison_plot,
        width = figure_width,
        height = figure_height
)


ggplot2::ggsave(
        filename = here::here(
                "results",
                "figures",
                "comparison-plot.png"
        ),
        plot = payoff_maximizing_model_comparison_plot,
        width = figure_width,
        height = figure_height,
        dpi = figure_dpi
)
```

# GLMM Diagnostics

## Payoff Maximizing Choice Model

```{r}
set.seed(123)
payoff_maximizing_dharma <-
    DHARMa::simulateResiduals(
        fittedModel = final_payoff_maximizing_choice_model
    )

pdf(
        here::here(
                "results",
                "figures",
                "diagnostics",
                "payoff-maximizing-choice-DHARMa.pdf"
        ),
        width = 7,
        height = 5
)

plot(payoff_maximizing_dharma)

dev.off()

payoff_maximizing_uniformity_test <-
        DHARMa::testUniformity(
                payoff_maximizing_dharma
        )

payoff_maximizing_dispersion_test <-
        DHARMa::testDispersion(
                payoff_maximizing_dharma
        )

payoff_maximizing_outlier_test <-
        DHARMa::testOutliers(
                payoff_maximizing_dharma
        )

payoff_maximizing_uniformity_test
payoff_maximizing_dispersion_test
payoff_maximizing_outlier_test
```

## Choice Switching Model

```{r}
set.seed(123)
switch_dharma <-
        DHARMa::simulateResiduals(
                fittedModel = final_choice_switch_model
        )

pdf(
        here::here(
                "results",
                "figures",
                "diagnostics",
                "choice-switch-DHARMa.pdf"
        ),
        width = 7,
        height = 5
)

plot(switch_dharma)

dev.off()

switch_uniformity_test <-
        DHARMa::testUniformity(
                switch_dharma
        )

switch_dispersion_test <-
        DHARMa::testDispersion(
                switch_dharma
        )

switch_outlier_test <-
        DHARMa::testOutliers(
                switch_dharma
        )

switch_uniformity_test
switch_dispersion_test
switch_outlier_test
```

# LMM Diagnostics

## Reward Model

```{r}
reward_residual_plot <-
        plot_lmm_residuals(
                final_reward_model
        )


reward_qq_plot <-
        plot_lmm_qq(
                final_reward_model
        )


ggplot2::ggsave(
        filename = here::here(
                "results",
                "figures",
                "diagnostics",
                "reward-residuals.pdf"
        ),
        plot = reward_residual_plot,
        width = 7,
        height = 5
)


ggplot2::ggsave(
        filename = here::here(
                "results",
                "figures",
                "diagnostics",
                "reward-QQ.pdf"
        ),
        plot = reward_qq_plot,
        width = 7,
        height = 5
)
```

## Log RT Model

```{r}
log_rt_residual_plot <-
        plot_lmm_residuals(
                final_log_rt_model
        )


log_rt_qq_plot <-
        plot_lmm_qq(
                final_log_rt_model
        )


ggplot2::ggsave(
        filename = here::here(
                "results",
                "figures",
                "diagnostics",
                "log-rt-residuals.pdf"
        ),
        plot = log_rt_residual_plot,
        width = 7,
        height = 5
)


ggplot2::ggsave(
        filename = here::here(
                "results",
                "figures",
                "diagnostics",
                "log-rt-QQ.pdf"
        ),
        plot = log_rt_qq_plot,
        width = 7,
        height = 5
)
```

# Random-Effects Sensitivity Output

```{r}
random_effects_robustness <-
        tibble::tibble(

                model = c(
                        "quadratic_uncorrelated",
                        "quadratic_correlated"
                ),

                AIC = c(
                        AIC(payoff_maximizing_quadratic_uncorrelated),
                        AIC(payoff_maximizing_quadratic_correlated)
                ),

                BIC = c(
                        BIC(payoff_maximizing_quadratic_uncorrelated),
                        BIC(payoff_maximizing_quadratic_correlated)
                ),

                logLik = c(
                        as.numeric(
                                logLik(payoff_maximizing_quadratic_uncorrelated)
                        ),
                        as.numeric(
                                logLik(payoff_maximizing_quadratic_correlated)
                        )
                ),

                convergence = c(
                        model_convergence(
                                payoff_maximizing_quadratic_uncorrelated
                        ),
                        model_convergence(
                                payoff_maximizing_quadratic_correlated
                        )
                ),

                singularity = c(
                        model_singularity(
                                payoff_maximizing_quadratic_uncorrelated
                        ),
                        model_singularity(
                                payoff_maximizing_quadratic_correlated
                        )
                )
        ) |>
        dplyr::mutate(
                delta_AIC = AIC - min(AIC)
        )


random_effects_robustness

readr::write_csv(
        random_effects_robustness,
        here::here(
                "results",
                "tables",
                "random-effects-robustness.csv"
        )
)
```

# Quadratic Trial Sensitivity

```{r}
quadratic_robustness <-
        tibble::tibble(

                model = c(
                        "linear_interaction",
                        "quadratic_uncorrelated"
                ),

                AIC = c(
                        AIC(payoff_maximizing_interaction),
                        AIC(payoff_maximizing_quadratic_uncorrelated)
                ),

                BIC = c(
                        BIC(payoff_maximizing_interaction),
                        BIC(payoff_maximizing_quadratic_uncorrelated)
                ),

                logLik = c(
                        as.numeric(
                                logLik(payoff_maximizing_interaction)
                        ),
                        as.numeric(
                                logLik(payoff_maximizing_quadratic_uncorrelated)
                        )
                )
        ) |>
        dplyr::mutate(
                delta_AIC = AIC - min(AIC)
        )


quadratic_likelihood_ratio <-
        compare_nested_models(
                payoff_maximizing_linear_interaction_robustness,
                payoff_maximizing_quadratic_uncorrelated
        )


readr::write_csv(
        quadratic_robustness,
        here::here(
                "results",
                "tables",
                "quadratic-trial-robustness.csv"
        )
)


quadratic_robustness

quadratic_likelihood_ratio
```

# Overall Robustness Summary

```{r}
robustness_summary <-
        tibble::tibble(

                analysis = c(
                        "Random-effects specification",
                        "Trial functional form"
                ),

                comparison = c(
                        "Uncorrelated versus correlated random slope",
                        "Linear versus quadratic trial trajectory"
                ),

                criteria = c(
                        "AIC, BIC, logLik, likelihood-ratio test, convergence, singularity",
                        "AIC, BIC, logLik, likelihood-ratio test"
                )

        )


readr::write_csv(
        robustness_summary,
        here::here(
                "results",
                "tables",
                "robustness-summary.csv"
        )
)
```

# Computational Environment

```{r}
sessionInfo()
```
